Positive Results in Registered Reports

### 2020-01-09 manuscript.Rmd
Edited Tables 2 and 3 after rearranging the order of hypothesis introduction phrases, and made Table 3 smaller to fit on one page.

## Exploratory Analyses
As described in the Method section, we only classified close or direct replications of previously published work as replications. 
This means that our non-replication category also contains some conceptual replications and "internal" replications (where original and replication are published in the same paper). 
For ease of communication we will nonetheless refer to this category as "original" studies.
As expected, direct replications were much more common among Registered Reports than standard reports: `r n.rep.RR` out of `r n.RR` RRs ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` SRs ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work. 
However, this difference cannot account for the stark overall difference between SRs and RRs described above: 
Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(repproptest$statistic)`$, $p `r printp(repproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
```{r echo = FALSE, results = 'asis'}
apa_table(
  rep.table
  , digits = c(0, 0, 0, 2, 0, 0, 0, 2, 0)
  , col.names = c("", "n", "supported", "\\%", "95\\% CI", "n", "supported", "\\%", "95\\% CI")
  , align = c("l", rep("r", 8))
  , caption = "Positive results in original studies vs replication studies"
  , note = "SRs = standard reports, RRs = Registered Reports"
  , added_stub_head = "Variables"
  , col_spanners = list(`original studies` = c(2, 5), `replication studies` = c(6, 9))
)
```

@@

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.orig
  , digits = c(0, 0, 0, 0, 0)
  , col.names = c("core word(s)", "introduction phrase", "abstract", 
                  "full text", "total")
  , align = c("l", "l", rep("r", 3))
  , caption = "Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)"
  , note = "This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, 9 papers contributed two each, one contributed three, and one contributed four."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(3, 5))
  , midrules = c(6, 16, 22, 23, 27, 32)
  , landscape = FALSE
  , font_size = "footnotesize"
  , escape = TRUE
)
```

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.rep
  , digits = c(0, 0, 0, 0, 0)
  , col.names = c("core word(s)", "introduction phrase", "abstract", 
                  "full text", "total")
  , align = c("l", "l", rep("r", 3))
  , caption = "Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)"
  , note = "This table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no codeable hypothesis introduction. 30 papers contributed one phrase each, 7 papers contributed two each, and three contributed three each."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(3, 5))
  , midrules = c(4, 5, 6, 12, 16, 33, 34, 35, 36)
  , landscape = FALSE
  , font_size = "footnotesize"
  , escape = TRUE
)
```

>>>>

## Exploratory Analyses
As described in the Method section, we only classified close or direct replications of previously published work as replications. 
This means that our non-replication category also contains some conceptual replications and "internal" replications (where original and replication are published in the same paper). 
For ease of communication we will nonetheless refer to this category as "original" studies.
As expected, direct replications were much more common among Registered Reports than standard reports: `r n.rep.RR` out of `r n.RR` RRs ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` SRs ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work. 
However, this difference cannot account for the stark overall difference between SRs and RRs described above: 
Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
```{r echo = FALSE, results = 'asis'}
apa_table(
  rep.table
  , digits = c(0, 0, 0, 2, 0, 0, 0, 2, 0)
  , col.names = c("", "n", "supported", "\\%", "95\\% CI", "n", "supported", "\\%", "95\\% CI")
  , align = c("l", rep("r", 8))
  , caption = "Positive results in original studies vs replication studies"
  , note = "SRs = standard reports, RRs = Registered Reports"
  , added_stub_head = "Variables"
  , col_spanners = list(`original studies` = c(2, 5), `replication studies` = c(6, 9))
)
```

@@

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.orig
  , digits = c(0, 0, 0, 0, 0)
  , col.names = c("core word(s)", "introduction phrase", "abstract", 
                  "full text", "total")
  , align = c("l", "l", rep("r", 3))
  , caption = "Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)"
  , note = "This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(3, 5))
  , midrules = c(10, 16, 22, 23, 28, 32)
  , landscape = FALSE
  , font_size = "footnotesize"
  , escape = TRUE
)
```

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.rep
  , digits = c(0, 0, 0, 0, 0, 0, 0)
  , col.names = c("", "core word(s)", "introduction phrase", "abstract", 
                  "full text", "total", "")
  , align = c("l", "l", "l", rep("r", 4))
  , caption = "Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)"
  , note = "Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(4, 6))
  , midrules = c(6, 10, 11, 12, 29, 30, 34, 35, 36)
  , landscape = FALSE
  , font_size = "scriptsize"
  , escape = TRUE
)
```

### 2020-01-09 manuscript.tex
Edited Tables 2 and 3 after rearranging the order of hypothesis introduction phrases, and made Table 3 smaller to fit on one page.

For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
We downloaded a database of published RRs curated by the Center for Open Science{[}\^{}1{]} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
{[}\^{}1{]}: \url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}
Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS.
This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
Following these exclusions, we verified the RR status of all remaining papers in our sample.
Papers were counted as RRs if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig. 1).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d.).

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-8}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
\footnotesize{
\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes*, test* &  & 3 & 2 & 5\\
 & test of ... hypotheses & 0 & 1 & 1\\
 & test of ... hypothesis & 1 & 0 & 1\\
 & test the hypothesis that & 1 & 0 & 1\\
 & tested ... hypotheses & 0 & 1 & 1\\
 & tested the hypothesis that & 1 & 0 & 1\\ \midrule
hypothes* &  & 5 & 12 & 17\\
 & (Hypothesis 1) & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 2 & 2\\
 & Hypothesis 1: & 0 & 1 & 1\\
 & Hypothesis 1a (H1a): & 0 & 1 & 1\\
 & hypothesis was & 0 & 1 & 1\\
 & Hypothesis: & 0 & 1 & 1\\
 & hypothesize that & 0 & 3 & 3\\
 & hypothesized that & 4 & 2 & 6\\
 & registered ... hypotheses & 1 & 0 & 1\\ \midrule
test* &  & 5 & 2 & 7\\
 & test if & 0 & 1 & 1\\
 & test whether & 1 & 1 & 2\\
 & tested whether & 2 & 0 & 2\\
 & testing & 1 & 0 & 1\\
 & to ... test & 1 & 0 & 1\\ \midrule
test*, predict* & test ... prediction & 0 & 1 & 1\\ \midrule
predict* &  & 4 & 0 & 4\\
 & had ... predictions & 1 & 0 & 1\\
 & predicted that & 2 & 0 & 2\\
 & predicts that & 1 & 0 & 1\\ \midrule
examin* &  & 5 & 0 & 5\\
 & examine whether & 2 & 0 & 2\\
 & examined & 1 & 0 & 1\\
 & examined whether & 1 & 0 & 1\\
 & to examine & 1 & 0 & 1\\ \midrule
(other) &  & 0 & 5 & 5\\
 & (H1) & 0 & 1 & 1\\
 & expected that & 0 & 1 & 1\\
 & if ... then & 0 & 1 & 1\\
 & predication that & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, 9 papers contributed two each, one contributed three, and one contributed four.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-9}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
\footnotesize{
\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes*, test* &  & 2 & 1 & 3\\
 & test ... hypotheses & 0 & 1 & 1\\
 & test ... hypothesis & 1 & 0 & 1\\
 & tested ... hypotheses & 1 & 0 & 1\\ \midrule
hypothes*, predict* & hypotheses predicted & 1 & 0 & 1\\ \midrule
hypothes*, examin* & examined ... hypothesis & 1 & 0 & 1\\ \midrule
hypothes* &  & 2 & 5 & 7\\
 & according to ... hypothesis & 0 & 1 & 1\\
 & Hypotheses & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 1 & 1\\
 & hypothesize that & 0 & 1 & 1\\
 & hypothesized that & 2 & 1 & 3\\ \midrule
test* &  & 4 & 0 & 4\\
 & testing whether & 2 & 0 & 2\\
 & to ... test & 1 & 0 & 1\\
 & to test & 1 & 0 & 1\\ \midrule
replicat* &  & 20 & 3 & 23\\
 & aim ... to replicate & 0 & 1 & 1\\
 & aim at replicating & 1 & 0 & 1\\
 & aimed to replicate & 0 & 1 & 1\\
 & attempted to replicate & 1 & 0 & 1\\
 & attempts to replicate & 1 & 0 & 1\\
 & conducted ... replication & 3 & 0 & 3\\
 & conducted ... replications & 2 & 0 & 2\\
 & performed ... replication & 2 & 0 & 2\\
 & present ... replication & 1 & 0 & 1\\
 & present ... replications & 1 & 0 & 1\\
 & replicated ... experiment & 1 & 0 & 1\\
 & replicating & 0 & 1 & 1\\
 & report ... replication attempt & 1 & 0 & 1\\
 & report ... replications & 2 & 0 & 2\\
 & sought to replicate & 3 & 0 & 3\\
 & we replicated & 1 & 0 & 1\\ \midrule
replicat*, examin* & critically examine and replicate & 1 & 0 & 1\\ \midrule
predict* & predicted that & 2 & 0 & 2\\ \midrule
examin* & examine whether & 0 & 1 & 1\\ \midrule
(other) &  & 4 & 6 & 10\\
 & establish whether & 0 & 1 & 1\\
 & H1 & 0 & 2 & 2\\
 & investigate if & 1 & 0 & 1\\
 & sought to reproduce & 1 & 0 & 1\\
 & suggests that & 2 & 0 & 2\\
 & we ... conducted & 0 & 1 & 1\\
 & we assume & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} This table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no codeable hypothesis introduction. 30 papers contributed one phrase each, 7 papers contributed two each, and three contributed three each.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 RRs, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
Therefore we additionally tested how many of the RRs would have been detected in a regular search using our five most frequent word stems.
We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(68/71\) RRs (\(95.77 \%\)) would have been detected this way.
We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.

>>>>

For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
We downloaded a database of published RRs curated by the Center for Open Science{[}\^{}1{]} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
{[}\^{}1{]}: \url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}
Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS.
This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
Following these exclusions, we verified the RR status of all remaining papers in our sample.
Papers were counted as RRs if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig. 1).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing {[}(``Registered Replication Reports,'' n.d.); decision was not preregistered{]}.

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-8}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
\footnotesize{
\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes* &  & 5 & 12 & 17\\
 & (Hypothesis 1) & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 2 & 2\\
 & Hypothesis 1: & 0 & 1 & 1\\
 & Hypothesis 1a (H1a): & 0 & 1 & 1\\
 & hypothesis was & 0 & 1 & 1\\
 & Hypothesis: & 0 & 1 & 1\\
 & hypothesize that & 0 & 3 & 3\\
 & hypothesized that & 4 & 2 & 6\\
 & registered ... hypotheses & 1 & 0 & 1\\ \midrule
hypothes*, test* &  & 3 & 2 & 5\\
 & test of ... hypotheses & 0 & 1 & 1\\
 & test of ... hypothesis & 1 & 0 & 1\\
 & test the hypothesis that & 1 & 0 & 1\\
 & tested ... hypotheses & 0 & 1 & 1\\
 & tested the hypothesis that & 1 & 0 & 1\\ \midrule
test* &  & 5 & 2 & 7\\
 & test if & 0 & 1 & 1\\
 & test whether & 1 & 1 & 2\\
 & tested whether & 2 & 0 & 2\\
 & testing & 1 & 0 & 1\\
 & to ... test & 1 & 0 & 1\\ \midrule
test*, predict* & test ... prediction & 0 & 1 & 1\\ \midrule
examin* &  & 5 & 0 & 5\\
 & examine whether & 2 & 0 & 2\\
 & examined & 1 & 0 & 1\\
 & examined whether & 1 & 0 & 1\\
 & to examine & 1 & 0 & 1\\ \midrule
predict* &  & 4 & 0 & 4\\
 & had ... predictions & 1 & 0 & 1\\
 & predicted that & 2 & 0 & 2\\
 & predicts that & 1 & 0 & 1\\ \midrule
(other) &  & 0 & 5 & 5\\
 & (H1) & 0 & 1 & 1\\
 & expected that & 0 & 1 & 1\\
 & if ... then & 0 & 1 & 1\\
 & predication that & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-9}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
\scriptsize{
\begin{tabular}{lllrrrr}
\toprule
 &  &  & \multicolumn{3}{c}{source}  &\\
\cmidrule(r){4-6}
 & core word(s) & introduction phrase & abstract & full text & total & \\
\midrule
 & hypothes* &  & 2 & 5 & 7 & \\
 &  & according to ... hypothesis & 0 & 1 & 1 & \\
 &  & Hypotheses & 0 & 1 & 1 & \\
 &  & Hypothesis 1 (H1): & 0 & 1 & 1 & \\
 &  & hypothesize that & 0 & 1 & 1 & \\
 &  & hypothesized that & 2 & 1 & 3 & \\ \midrule
 & hypothes*, test* &  & 2 & 1 & 3 & \\
 &  & test ... hypotheses & 0 & 1 & 1 & \\
 &  & test ... hypothesis & 1 & 0 & 1 & \\
 &  & tested ... hypotheses & 1 & 0 & 1 & \\ \midrule
 & hypothes*, examin* & examined ... hypothesis & 1 & 0 & 1 & \\ \midrule
 & hypothes*, predict* & hypotheses predicted & 1 & 0 & 1 & \\ \midrule
 & replicat* &  & 20 & 3 & 23 & \\
 &  & aim ... to replicate & 0 & 1 & 1 & \\
 &  & aim at replicating & 1 & 0 & 1 & \\
 &  & aimed to replicate & 0 & 1 & 1 & \\
 &  & attempted to replicate & 1 & 0 & 1 & \\
 &  & attempts to replicate & 1 & 0 & 1 & \\
 &  & conducted ... replication & 3 & 0 & 3 & \\
 &  & conducted ... replications & 2 & 0 & 2 & \\
 &  & performed ... replication & 2 & 0 & 2 & \\
 &  & present ... replication & 1 & 0 & 1 & \\
 &  & present ... replications & 1 & 0 & 1 & \\
 &  & replicated ... experiment & 1 & 0 & 1 & \\
 &  & replicating & 0 & 1 & 1 & \\
 &  & report ... replication attempt & 1 & 0 & 1 & \\
 &  & report ... replications & 2 & 0 & 2 & \\
 &  & sought to replicate & 3 & 0 & 3 & \\
 &  & we replicated & 1 & 0 & 1 & \\ \midrule
 & replicat*, examin* & critically examine and replicate & 1 & 0 & 1 & \\ \midrule
 & test* &  & 4 & 0 & 4 & \\
 &  & testing whether & 2 & 0 & 2 & \\
 &  & to ... test & 1 & 0 & 1 & \\
 &  & to test & 1 & 0 & 1 & \\ \midrule
 & examin* & examine whether & 0 & 1 & 1 & \\ \midrule
 & predict* & predicted that & 2 & 0 & 2 & \\ \midrule
 & (other) &  & 4 & 6 & 10 & \\
 &  & establish whether & 0 & 1 & 1 & \\
 &  & H1 & 0 & 2 & 2 & \\
 &  & investigate if & 1 & 0 & 1 & \\
 &  & sought to reproduce & 1 & 0 & 1 & \\
 &  & suggests that & 2 & 0 & 2 & \\
 &  & we ... conducted & 0 & 1 & 1 & \\
 &  & we assume & 0 & 1 & 1 & \\
 &  & we expect & 0 & 1 & 1 & \\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 RRs, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
Therefore we additionally tested how many of the RRs would have been detected in a regular search using our five most frequent word stems.
We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) RRs (\(97.18 \%\)) would have been detected this way.
We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.
